Community Data Science meets Digital Heritage: Controversies about World Heritage Sites in the Online Community of Wikipedia

### 2019-05-08 code/paper.Rmd
consumption of articles

## Basic qualitites of attention paid to articles

@@

  ggplot(page_data_for_all_pages_attent_long,
         aes(value)) +
  geom_density(aes(fill = source),
               alpha = 0.3) +
  scale_x_log10() +
  scale_fill_viridis_d() +
  facet_wrap( ~ variable, 
              scales = "free",
              labeller = labeller) +
  theme_minimal() +
    ggtitle("Basic qualities about attention given to Wikipedia articles")

ggsave("figures/wh_wikpedia_pages_attention_given.png")
```

>>>>

## Basic qualities of consumption of articles

@@

  ggplot(page_data_for_all_pages_attent_long,
         aes(value)) +
  geom_density(aes(fill = source),
               alpha = 0.3) +
  scale_x_log10() +
  scale_fill_viridis_d() +
  facet_wrap( ~ variable, 
              scales = "free",
              labeller = labeller) +
  theme_minimal() +
    ggtitle("Basic qualities about consumption of Wikipedia articles")

ggsave("figures/wh_wikpedia_pages_consumption.png")
```
